Embedding Dimension of Polyhedral Losses

### 2020-01-31 colt-20/embed-dim.tex
Making images smaller to fit equations on same page
conc

\section{Discussion} \label{sec:conclusion}
\raf{
We conjecture that this continues to hold in higher dimensions.\bo{Formalize conjecture later?}
In other words, we conjecture that embedding dimension is actually always equal to the more permissive \emph{convex calibration dimension} of \cite{ramaswamy2016convex}.}

\paragraph{Comparison to feasible subspace dimension.}
Essentially the only other known lower-bound technique for dimensionality of calibrated surrogates is the \emph{feasible subspace dimension} of \cite{ramaswamy2016convex}.
\bo{TMI?}
This crux of this technique is also an optimality condition on a surrogate loss, showing that if $0$ is in the $p$-weighted Minkowski sum of $L$'s subgradient sets, then there is some local ``flat'' (affine set) of dimension $n-d-1$ such that $0$ is also in the $p'$-weighted Minkowski sum for all $p'$ in the flat.
This implies the flat must be contained in every level set $\gamma_r$ that $p$ is in.
Therefore, for example, if the intersection of several level sets is a single vertex $v$ (as in e.g. the $0-1$ loss on $n$ outcomes for the uniform distribtion), then the only such flat can be of dimension $0$, which gives a $d \geq n-1$ lower bound.

Thus, although feasible subspace dimension applies to any convex surrogate, the relation to our techniques is an interesting future direction.
The advantage of our approach for generic $d$ is that our optimality conditions and quadratic feasibility program consider the structure of the entire level set $\gamma_r$, rather than just a single witness point.
This allows us to prove lower bounds on the abstain loss for $\alpha \leq 1/2$, which feasible subspace dimension cannot.
Proving the following conjecture would even more closely relate the two techniques (a disproof would also be extremely interesting):
\begin{conjecture}\label{conj:embed-equals-ccdim}
  If a discrete loss $\ell$ has a $d$-dimensional calibrated convex surrogate, then it is $d$-embeddable (i.e. has a $d$-dimensional calibrated polyhedral surrogate).
  In other words, embedding dimension always equals convex calibration dimension~\citep{ramaswamy2016convex}.
\end{conjecture}
Our results show the conjecture is true when $d=1$.

\paragraph{Future Work.}
There are a few threads of future work: the first is to utilize monotonicity to see if we can construct even tighter lower bounds on embedding dimension.
Second, we hope to understand when, if ever, embedding dimension is not equal to convex calibration dimension, as stated in Conjecture~\ref{conj:embed-equals-ccdim}.
Moreover, the restriction that we are calibrated over the entire simplex may be tighter than necessary in some contexts, and would be useful to understand the tradeoff between calibration and dimension of a surrogate loss.
For one example where we can reduce surrogate dimension with a low-entropy assumption on the simplex, see~\cite[Example 6]{agarwal2015consistent}.

>>>>

\section{Discussion} \label{sec:conclusion}

Essentially the only other known lower-bound technique for dimensionality of calibrated surrogates is the \emph{feasible subspace dimension} of \cite{ramaswamy2016convex}.
This crux of this technique is also an optimality condition on a surrogate loss, showing that if $0$ is in the $p$-weighted Minkowski sum of the subgradient sets of $L$, then there is some local affine set of dimension $n-d-1$ such that $0$ is also in the $p'$-weighted Minkowski sum for all $p'$ in the set, and thus the set must be contained in $\gamma_r$.
% This implies the flat must be contained in every level set $\gamma_r$ that $p$ is in.
Therefore, for example, if the intersection of several level sets is a single vertex $v$ (as in e.g. 0-1 loss for the uniform distribtion), then the only such set can be of dimension $0$, which gives a $d \geq n-1$ lower bound.

Thus, although feasible subspace dimension applies to any convex surrogate, the relation to our techniques is an interesting future direction.
The advantage of our approach for generic $d$ is that our optimality conditions and quadratic feasibility program consider the structure of the entire level set $\gamma_r$, rather than just a single witness point.
This allows us to prove lower bounds on the abstain loss for $\alpha \leq 1/2$, while feasible subspace dimension cannot.
Proving the following conjecture would even more closely relate the two techniques (a disproof would also be extremely interesting):
\begin{conjecture}\label{conj:embed-equals-ccdim}
  If a discrete loss $\ell$ has a $d$-dimensional calibrated convex surrogate, then it is $d$-embeddable (i.e. has a $d$-dimensional calibrated polyhedral surrogate).
  In other words, embedding dimension always equals convex calibration dimension.%~\citep{ramaswamy2016convex}.
\end{conjecture}
Our results show the conjecture is true when $d=1$.

\paragraph{Future Work.}
There are a few threads of future work: the first is to utilize monotonicity to see if we can construct even tighter lower bounds on embedding dimension.
Second, we hope to understand when, if ever, embedding dimension is not equal to convex calibration dimension, as stated in Conjecture~\ref{conj:embed-equals-ccdim}.
Moreover, the restriction that we are calibrated over the entire simplex may be tighter than necessary in some contexts, and would be useful to understand the tradeoff between calibration and dimension of a surrogate loss.
For one example where we can reduce surrogate dimension with a low-entropy assumption on the simplex, see~\citet[Example 6]{agarwal2015consistent}.
